Inference of proto-neutron star properties from gravitational-wave data in core-collapse supernovae

### 2020-11-10 ccsn.tex
Fixing typo in the acknowledgements.

\bigskip\noindent\textit{Acknowledgments.--} Work supported by the Spanish Agencia Estatal de Investigaci\'on (PGC2018-095984-B-I00), by the Generalitat Valenciana (PROMETEO/2019/071) and by the European Union’s Horizon 2020 research and innovation (RISE) programme H2020-MSCA-RISE-2017 GrantNo. FunFiCO-777740.
N.C. acknowledges support from National Science Foundation grant PHY-1806990.
R.M. gratefully acknowledges support by the James Cook Fellowship from Government funding, administered by the Royal Society Te  Ap\={a}rangi. R.M. and P.M.-R. also acknowledge funding from  DFG Grant KI 1443/3-2 and thank the Centre for eResearch at the University of Auckland for their technical support.
P.C.-D. acknowledges the support of the Spanish {\it Ramon y Cajal} programme (RYC-2015-19074) supporting his research.
\begin{appendices}
\input{appendixA}
\end{appendices}
%\bibliographystyle{unsrt}
\bibliography{biblio}

>>>>

\bigskip\noindent\textit{Acknowledgments.--} Work supported by the Spanish Agencia Estatal de Investigaci\'on (PGC2018-095984-B-I00), by the Generalitat Valenciana (PROMETEO/2019/071) and by the European Union’s Horizon 2020 research and innovation (RISE) programme (H2020-MSCA-RISE-2017 GrantNo. FunFiCO-777740).
N.C. acknowledges support from National Science Foundation grant PHY-1806990.
R.M. gratefully acknowledges support by the James Cook Fellowship from Government funding, administered by the Royal Society Te  Ap\={a}rangi. R.M. and P.M.-R. also acknowledge funding from  DFG Grant KI 1443/3-2 and thank the Centre for eResearch at the University of Auckland for their technical support.
P.C.-D. acknowledges the support of the Spanish {\it Ramon y Cajal} programme (RYC-2015-19074) supporting his research.
\begin{appendices}
\input{appendixA}
\end{appendices}
%\bibliographystyle{unsrt}
\bibliography{biblio}
